The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-24 paper.tex
fine tuning after merging

% JULIA: brief problem definition / issue, motivation, objectives, contribution ...

@@

\begin{figure}[hb]
    \centering
    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
    \caption{Activities with the robot over time, n = 9 households. This bar
        chart shows how many of the 9 households carried out different kinds of
        anthropomorphic / social activities with and related to the robot at 3
        time points during 6 months. Activities include \texttt{watching} the
        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
        \texttt{talking} to the robot, \texttt{playing} with the robot.
        Participants were asked to report on these activities at 3 time points
        after the robot was deployed in their home: after 2 weeks, after 2 months,
        and after 6 months.}

@@

\begin{figure}[b]
    \centering
    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}

    \begin{tikzpicture}[scale=0.5, y = 2cm]
    %axis
    \draw (0,0) -- coordinate (x axis mid) (20,0);
    \draw (0,0) -- coordinate (y axis mid) (0,7);
    %ticks
    \foreach \x in {0,4,...,20}
        \draw (\x,1pt) -- (\x,-3pt);
    \foreach \y in {1,...,7} 
        \draw[black!20] (20,\y) -- (-3pt,\y);
    \foreach \y in {1,...,7} 
        \draw (-3pt, \y) node[anchor=east] {\y}; 
    %labels
    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
    \node at (2, -0.4) {\tiny expectations};
    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};

@@

    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.

    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
\end{enumerate}

\begin{figure}[b]
    \centering
    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc. iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
    \label{fig:aibo-roomba-ipad}
\end{figure}

@@

Overall, findings of the content analysis suggest that there are differences in
people's tendency to use anthropomorphic language, originating form the design
characteristics of the artifact. Interestingly, not only the physical embodiment
of the object but also the interaction complexity and purpose of use of the
object seems to play a role in how far the object is anthropomorphized.

@@

Anthropomorphism is an interesting phenomenon because it tells us something about 
the relationship between the human who anthropomorphizes, and the non-human agent 
which is anthropomorphized. Though commonly observed, it appears controversial, at 
the same time, that humans tend to \hl{\textit{``see human in the non-
human''}}. 
Anthropomorphism as a social phenomenon arises in an interaction 
\citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
partners (the human and the real or imagined non-human agent). Therefore, one can 
take two main perspectives on explaining it \citep{lee_human_2005}: an artifact-
centered, and a human-centered. We briefly outline both views in the following. 
It has to be kept in mind that both perspectives are inseparable; they apply at the 
same time, and we would like to present them here just as two different viewpoints 
on the same kind of phenomenon.

@@

More concretely, it has been found that the appearance and function of a impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}. Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit
confusing...}.

>>>>

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
    \caption{Activities with the robot over time, n = 9 households. This bar
        chart shows how many of the 9 households carried out different kinds of
        anthropomorphic / social activities with and related to the robot at 3
        time points during 6 months. Activities include \texttt{watching} the
        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
        \texttt{talking} to the robot, \texttt{playing} with the robot.
        Participants were asked to report on these activities at 3 time points
        after the robot was deployed in their home: after 2 weeks, after 2 months,
        and after 6 months.}

@@

\begin{figure}
    \centering
%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}

    \begin{tikzpicture}[scale=0.5, y = 2cm]
    %axis
    \draw (0,0) -- coordinate (x axis mid) (20,0);
    \draw (0,0) -- coordinate (y axis mid) (0,7);
    %ticks
    \foreach \x in {0,4,...,20}
        \draw (\x,1pt) -- (\x,-3pt);
    \foreach \y in {1,...,7} 
        \draw[black!20] (20,\y) -- (-3pt,\y);
    \foreach \y in {1,...,7} 
        \draw (-3pt, \y) node[anchor=east] {\y}; 
    %labels
    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
    \node at (2, -0.4) {\tiny expectations};
    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};

@@

\begin{enumerate}
    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
\end{enumerate}

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc. iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
    \label{fig:aibo-roomba-ipad}
\end{figure}

@@

Overall, findings of the content analysis suggest that there are differences in
people's tendency to use anthropomorphic language, originating form the design
characteristics of the artifact. A pet-like robot encourages people to use more 
anthropomorphic expressions when discussing about it in an online forum. However, 
the difference might also be related to other factors that we did not analyze 
here (\eg. author's characteristics). Our analysis further shows that the design 
of the robot seems to more important than the topic of the discussion. 
Interestingly, not only the physical embodiment
of the object but also the interaction complexity and purpose of use of the
object seems to play a role in how far the object is anthropomorphized.

@@

Anthropomorphism is an interesting phenomenon because it tells us something about 
the relationship between the human who anthropomorphizes, and the non-human agent 
which is anthropomorphized. Though commonly observed, it appears controversial, at 
the same time, that humans tend to \textit{``see human in the non-
human''} \citep{epley_seeing_2007}. 
Anthropomorphism as a social phenomenon arises in an interaction 
\citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
partners (the human and the real or imagined non-human agent). Therefore, one can 
take two main perspectives on explaining it \citep{lee_human_2005}: an artifact-
centered, and a human-centered. We briefly outline both views in the following. 
It has to be kept in mind that both perspectives are inseparable; they apply at the 
same time, and we would like to present them here just as two different viewpoints 
on the same kind of phenomenon.

@@

The domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
